---
title: "Bot Sleuth_3.11.2026"
author: "Abbie Clapp and Michelle Marji"
date: "2026-03-11"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Packages
library(httr)
library(jsonlite)
library(purrr)
library(maps)
library(scales)
library(tidyverse)
library(tibble)
library(tidyr)
```

## Create IP Address Data
### Source: https://www.webpagetest.org/addresses.php

```{r,eval=F}
ip_locations_raw <- tribble(
  ~location_id, ~location_name, ~country, ~ip_address,
  "IAD_US_01", "Dulles, Virginia", "USA", "34.21.9.50",
  "SLC_US_02", "Salt Lake City, Utah", "USA", "34.106.208.213",
  "LAX_US_01", "Los Angeles, California", "USA", "34.94.159.140",
  "YYZ_CA_01", "Toronto", "Canada", "34.130.107.20",
  "GRU_BR_01", "Sao Paulo", "Brazil", "34.39.131.22",
  "DUB_IE_01", "Dublin", "Ireland", "18.203.101.63, 52.208.1.171, 34.240.49.81",
  "LHR_GB_01", "London", "United Kingdom", "35.242.177.6",
  "CDG_FR_01", "Paris", "France", "13.36.154.207",
  "AMS_NL_02", "Amsterdam", "Netherlands", "34.91.238.70",
  "FRA_DE_02", "Frankfurt", "Germany", "34.159.56.80",
  "MXP_IT_01", "Milan", "Italy", "34.154.170.5",
  "QVZ_FI_01", "Hamina", "Finland", "35.228.243.201",
  "CPT_ZA_01", "Cape Town", "South Africa", "13.246.114.251",
  "BAH_BH_01", "Bahrain", "Bahrain", "15.184.48.78",
  "DXB_AE_01", "Dubai", "UAE", "20.74.211.96, 20.233.37.119, 20.233.19.247, 74.243.255.151, 20.216.56.115",
  "BOM_IN_01", "Mumbai", "India", "43.204.105.75",
  "SIN_SG_01", "Singapore", "Singapore", "34.124.137.169",
  "BKK_TH_01", "Bangkok", "Thailand", "43.133.118.155, 43.133.103.102",
  "CGK_ID_01", "Jakarta", "Indonesia", "34.101.194.174",
  "HKG_CN_01", "Hong Kong", "China", "34.92.96.4",
  "PVG_CN_04", "Shanghai", "China", "42.192.58.21, 81.69.231.117",
  "BJS_CN_04", "Beijing", "China", "43.138.124.228, 82.156.238.27, 82.156.71.105, 101.43.244.140",
  "TPE_TW_01", "Taiwan", "Taiwan", "104.199.223.119",
  "HET_CN_01", "Hohhot", "China", NA,
  "ICN_KR_01", "Seoul", "South Korea", "43.200.31.191",
  "NRT_JP_01", "Tokyo", "Japan", "34.84.123.12",
  "ITM_JP_01", "Osaka", "Japan", "13.208.89.86",
  "SYD_AU_01", "Sydney", "Australia", "34.40.137.12",
  "MEL_AU_03", "Melbourne", "Australia", "13.70.181.210, 20.11.145.57, 4.200.141.43, 4.199.33.8, 20.213.214.56",
  "LAX_US_05", "Los Angeles (M1 Mac Mini)", "USA", NA
)
```

### Additional example data with geolocation data included

#### Source: https://github.com/ipinfo/sample-database/blob/main/IP%20Geolocation/ip_geolocation_sample.csv

```{r}
ip_locations_raw <- read_csv("ip_geolocation_sample_edited.csv")
```

# Initial IP Address Analyses

```{r}
# duplicate ip addresses (count)
ip_locations_raw |>
  count(ip_address) |>
  filter(n > 1)

# duplicates ip addresses (data table)
dup_ip <- ip_locations_raw |>
  group_by(ip_address) |>
  filter(n() > 1) |>
  ungroup()                   

# duplicate locations (data table)
dup_coords <- ip_locations_raw |>
  group_by(location_latitude, location_longitude) |>
  filter(n() > 1) |>
  ungroup()

# add a count variable to dup_coords
dup_coords <- dup_coords |>
  add_count(location_latitude, location_longitude, name = "dup_coords_count")

# count coord frequency
loc_counts <- ip_locations_raw |>
  count(location_latitude, location_longitude, name = "freq") |>
  arrange(desc(freq))
```

```{r}
loc_counts$location_latitude  <- as.numeric(loc_counts$location_latitude)

loc_counts$location_longitude <- as.numeric(loc_counts$location_longitude)

# graph locations to find outside of the US
world <- map_data("world")

ggplot() +
  geom_map(data = world, map = world,
           aes(long, lat, map_id = region),
           fill = "grey95", color = "grey80", linewidth = 0.2) +
  geom_point(data = loc_counts,
             aes(x = location_longitude, y = location_latitude, size = freq),
             alpha = 0.6) +
  scale_size_area(max_size = 16, breaks = pretty_breaks(5)) +
  coord_quickmap() +
  labs(
    title = "Survey Response Approximate Locations (Point Size = Frequency)",
    x = "Longitude", y = "Latitude", size = "Responses"
  ) +
  theme_minimal(base_size = 12)

```

# Checking ISPs

## Prepping Data

```{r}
# --------------------------------
# Normalize into one IP per row
# --------------------------------
ip_data <- ip_locations_raw |>
  filter(!is.na(ip_address)) |>
  separate_rows(ip_address, sep = ",") |>
  mutate(
    query = stringr::str_trim(ip_address)
  ) |>
  dplyr::select(
    query,
    location_latitude,
    location_longitude
  )

ip_data
```

```{r, eval=F}
## only include unique ip addresses
ip_data <- unique(ip_data)

## make an ip address list
ip_data_list <- ip_data |>
  dplyr::pull(query) |>
  as.character() |>
  stringr::str_trim()
ip_data_list
```

## APIs

### IP-API 

Batch lookup on ip-api (100 per request per ip-api free docs)

```{r}
to_query_objects <- function(ip_vec) {
  lapply(ip_vec, function(x) list(query = x))
}

lookup_batch_ipapi <- function(chunk_vec) {
  body_json <- jsonlite::toJSON(to_query_objects(unname(chunk_vec)), auto_unbox = TRUE)
  
  res <- httr::POST(
    url    = "http://ip-api.com/batch?fields=status,message,query,country,countryCode,region,regionName,city,lat,lon,isp,org,as,proxy,hosting,mobile",
    body   = body_json,
    encode = "raw",
    httr::add_headers(`Content-Type` = "application/json"),
    httr::timeout(10)
  )
  httr::stop_for_status(res)
  
  out <- jsonlite::fromJSON(httr::content(res, "text", encoding = "UTF-8"), flatten = TRUE)
  tibble::as_tibble(out)
}

chunks_100 <- split(ip_data$query, ceiling(seq_along(ip_data$query) / 100))

results_ipapi <- purrr::map_dfr(chunks_100, \(ch) {
  tryCatch(
    lookup_batch_ipapi(ch),
    error = function(e) {
      warning("ip-api batch failed: ", conditionMessage(e))
      tibble::tibble(status = "fail", message = conditionMessage(e), query = ch)
    }
  )
})
results_ipapi
```

### IP Info

(≤100 per request)

source: https://ipinfo.io/developers

```{r}
token <- "255a01dbca9d6e" # publicly available on their website

# look up on ipinfo.io - help function
lookup_ipinfo <- function(chunk_vec, token) {
  # ipinfo has a batch endpoint at /batch
  url <- paste0("https://ipinfo.io/batch?token=", token)
  
  # body is a JSON array of IPs
  body_json <- jsonlite::toJSON(as.list(chunk_vec), auto_unbox = TRUE)
  
  res <- httr::POST(
    url,
    body = body_json,
    encode = "raw",
    httr::add_headers(`Content-Type` = "application/json")
  )
  httr::stop_for_status(res)
  
  out <- jsonlite::fromJSON(httr::content(res, "text", encoding = "UTF-8"))
  
  # convert nested list to tibble
  tibble::enframe(out, name = "query", value = "info") %>%
    tidyr::unnest_wider(info)
}

ip_vec <- ip_data |>
  pull(query) |>                
  as.character() |>
  na.omit() |>
  unique()

# look up on ipinfo.io - run in chunks
chunks <- split(ip_vec, ceiling(seq_along(ip_vec) / 100))

results_ipinfo <- purrr::map_dfr(chunks, \(ch) {
  tryCatch(
    lookup_ipinfo(ch, token),
    error = function(e) {
      warning("Batch failed: ", conditionMessage(e))
      tibble(query = ch, error = conditionMessage(e))
    }
  )
})
results_ipinfo
```

### Free IP API

No Key - limited to 60 request/min 

**Note:** Sometimes I comment out the sys.Sleep() line since it makes it take awhile to run the code, but note that it won't get the IP info for all rows when this is the case.

```{r}
lookup_freeipapi_one <- function(ip) {
  url <- paste0("https://freeipapi.com/api/json/", ip)

  res <- httr::GET(url, httr::timeout(15))
  httr::stop_for_status(res)

  x <- jsonlite::fromJSON(
    httr::content(res, "text", encoding = "UTF-8"),
    simplifyVector = TRUE
  )

  # drop only what you do not want
  x[c("timeZones", "zipCode")] <- NULL

  # keep only simple scalar fields
  x <- x[vapply(x, function(z) length(z) == 1 && !is.list(z), logical(1))]

  # force to character so bind_rows won't fail on mixed types
  x <- lapply(x, as.character)

  tibble::as_tibble(x) |>
    dplyr::rename(query = dplyr::any_of("ipAddress"))
}

lookup_freeipapi_bulk <- function(ip_vec) {
  purrr::map_dfr(as.character(ip_vec), function(ip) {
    tryCatch(
      lookup_freeipapi_one(ip),
      error = function(e) {
        tibble::tibble(
          query = ip,
          error = conditionMessage(e)
        )
      }
    )
  })
}

chunks <- split(ip_vec, ceiling(seq_along(ip_vec) / 60))

results_freeipapi <- purrr::map_dfr(chunks, \(ch) {
  tryCatch(
    lookup_freeipapi_bulk(ch),
    error = function(e) {
      warning("Batch failed: ", conditionMessage(e))
      tibble(query = ch, error = conditionMessage(e))
    }
    # ,
    #     Sys.sleep(120)
  )
})
results_freeipapi
```

### IP Query

No key. Limit 10,000 IPs per batch.

**Note:** Could see if this method works for the other APIs and if so change to this since it's more concise

```{r}
ips_flat <- str_flatten(ip_data$query,collapse = ",")
url_ip_query <- 
  paste("https://api.ipquery.io/", ips_flat, sep = "")

results_ip_query <- GET(url_ip_query)
results_ip_query

results_ip_query <- fromJSON(rawToChar(results_ip_query$content))
results_ip_query

results_ip_query <- do.call(data.frame, results_ip_query)
results_ip_query <- results_ip_query %>% rename(query = ip)
```

**Note:** Having issue here where I get an error when running all together, but when I sepcifically run this chunk it works

## Combine all results

```{r}
combined_results <- results_ipapi |>
  dplyr::rename_with(~ paste0("ipapi_", .), -query) |>
  dplyr::full_join(
    results_ipinfo |>
      dplyr::rename_with(~ paste0("ipinfo_", .), -query),
    by = "query"
  ) |>
  dplyr::full_join(
    results_ip_query |>
      dplyr::rename_with(~ paste0("ipquery_", .), -query),
    by = "query"
  ) |>
  dplyr::full_join(
    results_freeipapi |>
      dplyr::rename_with(~ paste0("freeipapi_", .), -query),
    by = "query"
  )

combined_results
```
## Will want to note for users of the code that they'll likely need to update this based on their data - we are just including suspicious hosts we commonly see. Or maybe shouldn't include specific hosts at all? Not sure

## Suspicious Host Flagging

**Note:** I looked into anycast, but not fully sure if that's something that would be suspicious. Sounds like it involves multiple servers showing up as the same IP address but not sure if that's something people would be using for suss survey things.

Including Tor since it seems to be used purposefully to hide your information on the internet

One var is character instead of logical for some reason:

```{r}
combined_results$freeipapi_isProxy <- as.logical(combined_results$freeipapi_isProxy)
class(combined_results$freeipapi_isProxy)
```


```{r}
host_cols <- combined_results %>% select(ipapi_hosting,ipapi_proxy,ipapi_hosting,ipquery_risk.is_tor,ipquery_risk.is_proxy,ipquery_risk.is_datacenter,freeipapi_isProxy)

# Source - https://stackoverflow.com/a/66365618
# Posted by Waldi, modified by community. See post 'Timeline' for change history
# Retrieved 2026-04-19, License - CC BY-SA 4.0

host_total <- # change to add mutate
combined_results %>%
  rowwise() %>% 
       summarize(host_total = 
                   sum(c(ipapi_hosting,ipapi_proxy,ipapi_hosting,ipquery_risk.is_tor,ipquery_risk.is_proxy,ipquery_risk.is_datacenter,freeipapi_isProxy,ipquery_risk.is_vpn),na.rm=T))

combined_results$host_total <- host_total
```

### Specific Names

**Note:** Could update these based on what we see with the VPNs/bot, but then obviously it's going to be effective lol. Not sure how to approach this. The ones I have here are just ones I've seen in datasets I've worked with, but I don't have any strong evidence that they're problematic.


# add lines for each of the IP lookups

# ideally change to make a loop going across all the ISP vars /more concise

```{r}
combined_results <- combined_results |>
  mutate(
    suspicious_host_ipapi_isp = if_else(
      str_detect(ipapi_isp, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"),TRUE, FALSE, missing = FALSE))

combined_results <- combined_results |>
  mutate(
    suspicious_host_ipapi_org = if_else(                     
        str_detect(ipapi_org, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"), TRUE, FALSE, missing = FALSE))

# in these data, ipapi_isp and ipapi_org seem to be the same

combined_results <- combined_results |>
  mutate(
    suspicious_host_ipapi_as = if_else(      
        str_detect(ipapi_as, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"), TRUE, FALSE, missing = FALSE))

combined_results <- combined_results |>
  mutate(
    suspicious_host_ipinfo = if_else(
      str_detect(ipinfo_org, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|Dedicated.com|PacketHub S.A.|PPPoX Pool"),TRUE, FALSE, missing = FALSE))
                    
combined_results <- combined_results |>
  mutate(
    suspicious_host_ipquery = if_else( 
          str_detect(ipquery_isp.isp, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"), TRUE, FALSE, missing = FALSE))

combined_results <- combined_results |>
  mutate(
    suspicious_host_freeipapi = if_else(
      str_detect(freeipapi_asnOrganization, "Amazon|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"),TRUE, FALSE, missing = FALSE))

```

Creating one flagging variable across the different IP API fields:

```{r}
combined_results <- 
combined_results %>% mutate(suspicious_host_ipapi_final = 
                              case_when(suspicious_host_ipapi_isp == T | 
                                        suspicious_host_ipapi_org == T |
                                        suspicious_host_ipapi_as == T
                                      ~ TRUE,
                                      TRUE ~ FALSE))
```


```{r}
susp_host_total <- # change to add mutate
combined_results %>%
  rowwise() %>% 
       summarize(susp_host_total = 
                   sum(c(suspicious_host_ipapi_final,suspicious_host_ipquery,suspicious_host_freeipapi),na.rm=T))

combined_results$susp_host_total <- susp_host_total
```

**Need to decide what reasonable threshold would be for this - of course people can change it for themselves though**

## Suspicious Location Flagging

```{r}
combined_results %>% select(ipapi_regionName,ipinfo_region,ipquery_location.state,suspicious_host_ipinfo)

combined_results %>% select(freeipapi_countryCode,
ipquery_location.country_code,
ipapi_countryCode,
ipinfo_country)
```

#### Country code variables:

freeipapi_countryCode
ipquery_location
ipapi_countryCode

ipinfo_country is equivalent to the country codes for the other lookup sites.

#### City variables:

ipapi_city
ipinfo_city
ipquery_location.city
freeipapi_cityName

### From Claude:
```{r}
# Helper: TRUE if either string contains the other (case-insensitive)
partial_match <- function(a, b) {
  mapply(function(x, y) {
    if (is.na(x) | is.na(y)) return(FALSE)
    grepl(x, y, ignore.case = TRUE) | grepl(y, x, ignore.case = TRUE)
  }, a, b)
}
```

```{r}
combined_results <- combined_results %>%
  mutate(
    city_match_1     = partial_match(ipquery_location.city, ipapi_city),
    city_match_2    = partial_match(ipquery_location.city, ipinfo_city),
    city_match_3 = partial_match(ipquery_location.city, freeipapi_cityName),
    city_match_4 = partial_match(ipapi_city, ipinfo_city),
    city_match_5 = partial_match(ipapi_city,freeipapi_cityName),
    city_match_6 = partial_match(ipinfo_city,freeipapi_cityName)
  )

combined_results %>% select(grep("city_match",names(combined_results)),ipquery_location.city,ipapi_city,ipinfo_city,freeipapi_cityName)
```

```{r,eval=F}
city_cols <- c("ipapi_city", "ipinfo_city", "freeipapi_cityName","ipquery_location.city")
```

**TBH I really don't remember what this is doing:**

```{r,eval=F}
for (col in city_cols) {
  new_col <- paste0("city_match_", col) # create new vars indicating city matches
  combined_results[[new_col]] <- partial_match( # in new cols, flag partial matches between ipquery_location.city and all other city vars
    combined_results$ipquery_location.city,
    combined_results[[col]]
  )
}
```

# Under construction :-) (4-27)



Flagging different match counts across the city columns:

```{r}
match_cols <- combined_results %>% select(city_match_1:city_match_6)
combined_results$city_match_n <- combined_results %>% select(city_match_1:city_match_6) %>% rowSums()

combined_results %>% select(city_match_n, city_match_1:city_match_6)
```

```{r}
# Any match across all sources
match_cols <- paste0("city_match_", city_cols)
combined_results$any_city_match <- rowSums(combined_results[match_cols]) > 0
```

```{r}
# 5+ (out of 6) matches across sources
combined_results$five_city_match <- rowSums(combined_results[match_cols]) > 1

combined_results %>% select(five_city_match, city_match_ipapi,ipquery_location.city,ipapi_city,freeipapi_cityName)
```

```{r}
# 4+ (out of 6) matches across sources
combined_results$four_city_match <- rowSums(combined_results[match_cols]) > 2

combined_results %>% select(grep("city_match",names(combined_results)),ipinfo_city,ipquery_location.city,ipapi_city,freeipapi_cityName,ipinfo_city)
```

```{r}
# 3+ (out of 6) matches across sources
combined_results$three_city_match <- rowSums(combined_results[match_cols]) > 3

combined_results %>% select(grep("city_match",names(combined_results)),ipinfo_city,ipquery_location.city,ipapi_city,freeipapi_cityName)
```

```{r}
# 2+ (out of 6) matches across sources
combined_results$two_city_match <- rowSums(combined_results[match_cols]) > 4

combined_results %>% select(grep("city_match",names(combined_results)),ipinfo_city,ipquery_location.city,ipapi_city,freeipapi_cityName)
```

```{r}
# 1+ (out of 6) matches across sources
combined_results$one_city_match <- rowSums(combined_results[match_cols]) > 5

combined_results %>% select(grep("city_match",names(combined_results)),ipinfo_city,ipquery_location.city,ipapi_city,freeipapi_cityName)


```

```{r}
combined_results %>% select(any_city_match:one_city_match)
```


#### Next steps (3/31/26)

Write code to apply same approach as for the cities above to region flagging.

--------------------

```{r}
# suspicious location flag
combined_results <- combined_results |>
  mutate(
    geo_outside_japan = (freeipapi_countryCode != "JP" | ipquery_location.country_code != "JP" | ipapi_countryCode != "JP" | ipinfo_country != "JP"),
    geo_disagree_region = (ipapi_regionName != ipinfo_region |
                      ipapi_regionName != ipquery_location.state | # seems kind of equivalent but not quite the same
                                            ipinfo_region != ipquery_location.state),
  # seems kind of equivalent but not quite the same
  geo_disagree_city = (
                      ipapi_city != ipinfo_city | 
                      ipapi_city != ipquery_location.city | 
                      ipinfo_city != ipquery_location.city |
                        freeipapi_cityName != ipapi_city |
                        freeipapi_cityName != ipinfo_city |
                        freeipapi_cityName != ipquery_location.city))

combined_results %>% select(geo_outside_japan,ipapi_country,ipinfo_country,ipquery_location.country) # in this instance, all of these are getting flagged

combined_results %>% select(geo_disagree_region,ipapi_regionName,ipinfo_region,ipquery_location.state)

combined_results %>% select(geo_disagree_city,ipapi_city,ipinfo_city,ipquery_location.city,freeipapi_cityName)

isp_counts <- bind_rows(
  combined_results |> count(ipapi_isp,  name = "n") |> rename(isp = ipapi_isp) |> mutate(source = "ipapi"),
  combined_results |> count(ipinfo_org, name = "n") |> rename(isp = ipinfo_org) |> mutate(source = "ipinfo")
)
isp_counts
```

**AC note:** A lot of the regions differ and are getting flagged. This is okay, but maybe should create count variables indicating whether there are discrepancies between 2 of the region variables, or all 3, etc. Either way, should definitely note that people should use caution with this.

Trying to do this:

```{r}
combined_results %>% mutate(geo_disagree_city_1 = case_when(ipapi_city != ipinfo_city ~ 1,
                                                            TRUE ~ 0))
                              
                              
                              
                              
                      #         (
                      # ipapi_city != ipinfo_city | 
                      # ipapi_city != ipquery_location.city | 
                      # ipinfo_city != ipquery_location.city |
                      #   freeipapi_cityName != ipapi_city |
                      #   freeipapi_cityName != ipinfo_city |
                      #   freeipapi_cityName != ipquery_location.city))

```


```{r}
combined_results %>% filter(grepl("Hiroshima", ipapi_city))
```

```{r}
# join to original data
d_ips <- ip_locations_raw |>
  mutate(ip_address = as.character(ip_address) |> str_trim()) |>
  left_join(combined_results, by = c("ip_address" = "query"))
d_ips
```

```{r}
# duplicate IP address flag
d_ips  <- d_ips  |>
  add_count(ip_address, name = "ip_count") |>
  mutate(dup_ip = ip_count > 1)
table(d_ips$dup_ip)

# check for clustering around the same finish time
# note: doesn't seem super useful
# time_clusters <- d_ips |>
#   group_by(duration_in_seconds) |>
#   summarise(count = n(), .groups = "drop") |>
#   arrange(desc(count))

# bot suspicion score
# note: I would add qualtrics relevantID/recaptcha and open-ended response flags to this (if available in your data)
d_ips <- d_ips |>
  mutate(
    bot_score = (suspicious_host + geo_outside_us + geo_disagree + dup_ip)
  )
table(d_ips$bot_score)
```

# Additional Sleuthing Steps

**AC note:**For now, I'm setting it not to run.

```{r,eval=F}
# open text as positive (less likely to be a bot)

## MM's version:
# d_ips <- d_ips |>
#   mutate(
#     n_open_text = rowSums(across(
#       c(park_do_5_text, metastereotype_8_text, stereotypes_8_text,
#         activities_do, activities_where, city_state, us_zip_code,
#         profession, feedback, free_stereotypes, free_stereotype_you,
#         soc_stereotypes_8_text, education_10_text),
#       ~ !is.na(.x) & .x != ""
#     ))
#   )

## AC's version (with OE variables from SES Data)
## do something else with this part? should this be added to bot score?
d_ips <- d_ips |>
  mutate(
    n_open_text = rowSums(across(
      c(ethnicity_5_text,
        gender_open,
        formative_yrs,
        political_orient_1,
        sex_orient_open,
        comments),
      ~ !is.na(.x) & .x != ""
    ))
  )
table(d_ips$n_open_text)

# AC: examine responses with 0 blank open-ended Qs
# **all of these response with 0 blank OEs either were screened out or otherwise did not finish**
# doesn't seem super useful
d_ips %>% filter(n_open_text==0) %>% select(ip_address,bot_score,suspicious_host,geo_outside_us,geo_disagree,dup_ip)
d_ips %>% filter(is.na(bot_score))
d_ips %>% filter(n_open_text>=1 & bot_score==0) 
d_ips %>% filter(n_open_text>=1 & bot_score<2) 
table(d_ips$n_open_text)

### iii. Qualtrics bot flagging tools

# RelevantID fraud score

# For fraud score, Qualtrics indicates that any score >30 is likely fraudulent and a bot. I'll also make a second flag to indicate any scores that are >0.

d_ips <- d_ips %>% mutate(rel_id_fraud_flag = ifelse(q_relevant_id_fraud_score >= 30, 
                                            TRUE,
                                            FALSE))
table(d_ips$rel_id_fraud_flag)

d_ips <- d_ips %>% mutate(rel_id_fraud_flag_0 = ifelse(q_relevant_id_fraud_score > 0, 
                                            TRUE,
                                            FALSE))
table(d_ips$rel_id_fraud_flag_0)

d_ips %>% filter(is.na(q_relevant_id_fraud_score)) # no missing scores

d_ips <- d_ips |>
  mutate(
    bot_score_relid = (suspicious_host + geo_outside_us + geo_disagree + dup_ip + rel_id_fraud_flag)
  )
table(d_ips$bot_score_relid)
table(d_ips$bot_score)
bot_ids_relid <- d_ips %>% filter(bot_score_relid>=2)
```

# Final Flagging

**Need to add looking across all the flagging variables to assess likelihood of bot/fraud**

```{r}
combined_results <- combined_results |>
  mutate(
    bot_score = (host_total + susp_host_total + )
  )
table(d_ips$bot_score)


combined_results <- combined_results |>
  mutate(
    bot_score = (suspicious_host + geo_outside_us + geo_disagree + dup_ip)
  )
table(d_ips$bot_score)



```


