---
title: "Bot Sleuth_3.11.2026"
author: "Abbie Clapp and Michelle Marji"
date: "2026-03-11"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Packages
library(httr)
library(jsonlite)
library(purrr)
library(maps)
library(scales)
library(tidyverse)
library(tibble)
library(tidyr)
```

## Create IP Address Data
### Source: https://www.webpagetest.org/addresses.php

```{r,eval=F}
ip_locations_raw <- tribble(
  ~location_id, ~location_name, ~country, ~ip_address,
  "IAD_US_01", "Dulles, Virginia", "USA", "34.21.9.50",
  "SLC_US_02", "Salt Lake City, Utah", "USA", "34.106.208.213",
  "LAX_US_01", "Los Angeles, California", "USA", "34.94.159.140",
  "YYZ_CA_01", "Toronto", "Canada", "34.130.107.20",
  "GRU_BR_01", "Sao Paulo", "Brazil", "34.39.131.22",
  "DUB_IE_01", "Dublin", "Ireland", "18.203.101.63, 52.208.1.171, 34.240.49.81",
  "LHR_GB_01", "London", "United Kingdom", "35.242.177.6",
  "CDG_FR_01", "Paris", "France", "13.36.154.207",
  "AMS_NL_02", "Amsterdam", "Netherlands", "34.91.238.70",
  "FRA_DE_02", "Frankfurt", "Germany", "34.159.56.80",
  "MXP_IT_01", "Milan", "Italy", "34.154.170.5",
  "QVZ_FI_01", "Hamina", "Finland", "35.228.243.201",
  "CPT_ZA_01", "Cape Town", "South Africa", "13.246.114.251",
  "BAH_BH_01", "Bahrain", "Bahrain", "15.184.48.78",
  "DXB_AE_01", "Dubai", "UAE", "20.74.211.96, 20.233.37.119, 20.233.19.247, 74.243.255.151, 20.216.56.115",
  "BOM_IN_01", "Mumbai", "India", "43.204.105.75",
  "SIN_SG_01", "Singapore", "Singapore", "34.124.137.169",
  "BKK_TH_01", "Bangkok", "Thailand", "43.133.118.155, 43.133.103.102",
  "CGK_ID_01", "Jakarta", "Indonesia", "34.101.194.174",
  "HKG_CN_01", "Hong Kong", "China", "34.92.96.4",
  "PVG_CN_04", "Shanghai", "China", "42.192.58.21, 81.69.231.117",
  "BJS_CN_04", "Beijing", "China", "43.138.124.228, 82.156.238.27, 82.156.71.105, 101.43.244.140",
  "TPE_TW_01", "Taiwan", "Taiwan", "104.199.223.119",
  "HET_CN_01", "Hohhot", "China", NA,
  "ICN_KR_01", "Seoul", "South Korea", "43.200.31.191",
  "NRT_JP_01", "Tokyo", "Japan", "34.84.123.12",
  "ITM_JP_01", "Osaka", "Japan", "13.208.89.86",
  "SYD_AU_01", "Sydney", "Australia", "34.40.137.12",
  "MEL_AU_03", "Melbourne", "Australia", "13.70.181.210, 20.11.145.57, 4.200.141.43, 4.199.33.8, 20.213.214.56",
  "LAX_US_05", "Los Angeles (M1 Mac Mini)", "USA", NA
)
```

### Additional example data with geolocation data included

#### Source: https://github.com/ipinfo/sample-database/blob/main/IP%20Geolocation/ip_geolocation_sample.csv

```{r}
ip_locations_raw <- read_csv("ip_geolocation_sample_edited.csv")
```

# Initial IP Address Analyses

```{r}
# duplicate ip addresses (count)
ip_locations_raw |>
  count(ip_address) |>
  filter(n > 1)

# duplicates ip addresses (data table)
dup_ip <- ip_locations_raw |>
  group_by(ip_address) |>
  filter(n() > 1) |>
  ungroup()                   

# duplicate locations (data table)
dup_coords <- ip_locations_raw |>
  group_by(location_latitude, location_longitude) |>
  filter(n() > 1) |>
  ungroup()

# add a count variable to dup_coords
dup_coords <- dup_coords |>
  add_count(location_latitude, location_longitude, name = "dup_coords_count")

# count coord frequency
loc_counts <- ip_locations_raw |>
  count(location_latitude, location_longitude, name = "freq") |>
  arrange(desc(freq))
```

```{r}
loc_counts$location_latitude  <- as.numeric(loc_counts$location_latitude)

loc_counts$location_longitude <- as.numeric(loc_counts$location_longitude)

# graph locations to find outside of the US
world <- map_data("world")

ggplot() +
  geom_map(data = world, map = world,
           aes(long, lat, map_id = region),
           fill = "grey95", color = "grey80", linewidth = 0.2) +
  geom_point(data = loc_counts,
             aes(x = location_longitude, y = location_latitude, size = freq),
             alpha = 0.6) +
  scale_size_area(max_size = 16, breaks = pretty_breaks(5)) +
  coord_quickmap() +
  labs(
    title = "Survey Response Approximate Locations (Point Size = Frequency)",
    x = "Longitude", y = "Latitude", size = "Responses"
  ) +
  theme_minimal(base_size = 12)

```

# Checking ISPs

## Prepping Data

```{r}
# --------------------------------
# Normalize into one IP per row
# --------------------------------
ip_data <- ip_locations_raw |>
  filter(!is.na(ip_address)) |>
  separate_rows(ip_address, sep = ",") |>
  mutate(
    query = stringr::str_trim(ip_address)
  ) |>
  dplyr::select(
    query,
    location_latitude,
    location_longitude
  )

ip_data
```

```{r, eval=F}
## only include unique ip addresses
ip_data <- unique(ip_data)

## make an ip address list
ip_data_list <- ip_data |>
  dplyr::pull(query) |>
  as.character() |>
  stringr::str_trim()
ip_data_list
```

## APIs

### IP-API 

Batch lookup on ip-api (100 per request per ip-api free docs)

```{r}
to_query_objects <- function(ip_vec) {
  lapply(ip_vec, function(x) list(query = x))
}

lookup_batch_ipapi <- function(chunk_vec) {
  body_json <- jsonlite::toJSON(to_query_objects(unname(chunk_vec)), auto_unbox = TRUE)
  
  res <- httr::POST(
    url    = "http://ip-api.com/batch?fields=status,message,query,country,regionName,city,lat,lon,isp,org,as,proxy,hosting,mobile",
    body   = body_json,
    encode = "raw",
    httr::add_headers(`Content-Type` = "application/json"),
    httr::timeout(10)
  )
  httr::stop_for_status(res)
  
  out <- jsonlite::fromJSON(httr::content(res, "text", encoding = "UTF-8"), flatten = TRUE)
  tibble::as_tibble(out)
}

chunks_100 <- split(ip_data$query, ceiling(seq_along(ip_data$query) / 100))

results_ipapi <- purrr::map_dfr(chunks_100, \(ch) {
  tryCatch(
    lookup_batch_ipapi(ch),
    error = function(e) {
      warning("ip-api batch failed: ", conditionMessage(e))
      tibble::tibble(status = "fail", message = conditionMessage(e), query = ch)
    }
  )
})
results_ipapi
```

### IP Info

(≤100 per request)

source: https://ipinfo.io/developers

```{r}
token <- "255a01dbca9d6e" # publicly available on their website

# look up on ipinfo.io - help function
lookup_ipinfo <- function(chunk_vec, token) {
  # ipinfo has a batch endpoint at /batch
  url <- paste0("https://ipinfo.io/batch?token=", token)
  
  # body is a JSON array of IPs
  body_json <- jsonlite::toJSON(as.list(chunk_vec), auto_unbox = TRUE)
  
  res <- httr::POST(
    url,
    body = body_json,
    encode = "raw",
    httr::add_headers(`Content-Type` = "application/json")
  )
  httr::stop_for_status(res)
  
  out <- jsonlite::fromJSON(httr::content(res, "text", encoding = "UTF-8"))
  
  # convert nested list to tibble
  tibble::enframe(out, name = "query", value = "info") %>%
    tidyr::unnest_wider(info)
}

ip_vec <- ip_data |>
  pull(query) |>                
  as.character() |>
  na.omit() |>
  unique()

# look up on ipinfo.io - run in chunks
chunks <- split(ip_vec, ceiling(seq_along(ip_vec) / 100))

results_ipinfo <- purrr::map_dfr(chunks, \(ch) {
  tryCatch(
    lookup_ipinfo(ch, token),
    error = function(e) {
      warning("Batch failed: ", conditionMessage(e))
      tibble(query = ch, error = conditionMessage(e))
    }
  )
})
results_ipinfo
```

### Free IP API

No Key - limited to 60 request/min 

```{r}
lookup_freeipapi_one <- function(ip) {
  url <- paste0("https://freeipapi.com/api/json/", ip)

  res <- httr::GET(url, httr::timeout(15))
  httr::stop_for_status(res)

  x <- jsonlite::fromJSON(
    httr::content(res, "text", encoding = "UTF-8"),
    simplifyVector = TRUE
  )

  # drop only what you do not want
  x[c("timeZones", "zipCode")] <- NULL

  # keep only simple scalar fields
  x <- x[vapply(x, function(z) length(z) == 1 && !is.list(z), logical(1))]

  # force to character so bind_rows won't fail on mixed types
  x <- lapply(x, as.character)

  tibble::as_tibble(x) |>
    dplyr::rename(query = dplyr::any_of("ipAddress"))
}

lookup_freeipapi_bulk <- function(ip_vec) {
  purrr::map_dfr(as.character(ip_vec), function(ip) {
    tryCatch(
      lookup_freeipapi_one(ip),
      error = function(e) {
        tibble::tibble(
          query = ip,
          error = conditionMessage(e)
        )
      }
    )
  })
}

# run lookup
results_freeipapi <- lookup_freeipapi_bulk(ip_data$query)
results_freeipapi

# run next set if stopped at 60
## create list of missing ip address rows
missing_ips <- results_freeipapi$query[is.na(results_freeipapi$capital)]

## run look up for next set
new_results <- lookup_freeipapi_bulk(missing_ips)
# new_results <- lookup_freeipapi_bulk_chunked(missing_ips)

## combine lists
results_freeipapi <- dplyr::rows_update(results_freeipapi, new_results, by = "query")
```


### IP Query

```{r}
ips_flat <- str_flatten(ip_data$query,collapse = ",")
url_ip_query <- 
  paste("https://api.ipquery.io/", ips_flat, sep = "")

results_ip_query <- GET(url_ip_query)
results_ip_query

results_ip_query <- fromJSON(rawToChar(results_ip_query$content))
results_ip_query

results_ip_query <- do.call(data.frame, results_ip_query)
results_ip_query <- results_ip_query %>% rename(query = ip)
```

## Combine all results

```{r}
combined_results <- results_ipapi |>
  dplyr::rename_with(~ paste0("ipapi_", .), -query) |>
  dplyr::full_join(
    results_ipinfo |>
      dplyr::rename_with(~ paste0("ipinfo_", .), -query),
    by = "query"
  ) |>
  dplyr::full_join(
    results_ip_query |>
      dplyr::rename_with(~ paste0("ipquery_", .), -query),
    by = "query"
  ) |>
  dplyr::full_join(
    results_freeipapi |>
      dplyr::rename_with(~ paste0("freeipapi_", .), -query),
    by = "query"
  )

combined_results
```
## Will want to note for users of the code that they'll likely need to update this based on their data - we are just including suspicious hosts we commonly see. Or maybe shouldn't include specific hosts at all? Not sure

## Suspicious Host Flagging

```{r}
# # suspicious host flag-original version
# combined_results <- combined_results |>
#   mutate(
#     suspicious_host = if_else(
#       str_detect(ipapi_isp, "Amazon|Google|Microsoft|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom") |
#         str_detect(ipinfo_org, "Amazon|Google|Microsoft|OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet| Europe|Korea Telecom"),
#       TRUE, FALSE, missing = FALSE
#     )
#   )

# # suspicious host flag-AC
## altering this to include hosts I see in this dataset, and remove google, amazon & microsoft
## also added additional fields to search in: ipapi_org, ipapi_as
combined_results <- combined_results |>
  mutate(
    suspicious_host = if_else(
      str_detect(ipapi_isp, "OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool") |
        str_detect(ipinfo_org, "OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
                     Dedicated.com|PacketHub S.A.|PPPoX Pool") |
        str_detect(ipapi_org, "OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool") |
        str_detect(ipapi_as, "OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool") |
          str_detect(ipquery_isp.isp, "OVH|DigitalOcean|Hetzner|Linode|Hosting|HostPapa|Turkcell Internet|Europe|Korea Telecom|Rackdog|iboss|IBOSS|Ducat|OVH SAS|Zscaler|ZSCALER|Datacamp|Cloudflare|InterLIR|Lietparkas UAB|HIVELOCITY, Inc.|Sneaker Server|GigeNet|Kaopu Cloud|SAP America|RingSquared CC|HostRoyale Technologies|Ipxo|	
Dedicated.com|PacketHub S.A.|PPPoX Pool"),
      TRUE, FALSE, missing = FALSE
    )
  )

combined_results$suspicious_host

## AC note: the invalid query ones are *not* getting flagged here
```
## Suspicious Location Flagging

```{r,eval=F}
# suspicious location flag
combined_results <- combined_results |>
  mutate(
    geo_outside_us = (ipapi_country != "United States" | ipinfo_country != "US" | ipquery_location.country != "United States"),
    geo_disagree = (ipapi_regionName != ipinfo_region |
                      ipapi_regionName != ipquery_location.state | # seems kind of equivalent but not quite the same
                                            ipinfo_region != ipquery_location.state | # seems kind of equivalent but not quite the same
                      ipapi_city != ipinfo_city | 
                      ipapi_city != ipquery_location.city | 
                      ipinfo_city != ipquery_location.city)
  )

combined_results$geo_disagree # in this instance, all of these are getting flagged

isp_counts <- bind_rows(
  combined_results |> count(ipapi_isp,  name = "n") |> rename(isp = ipapi_isp) |> mutate(source = "ipapi"),
  combined_results |> count(ipinfo_org, name = "n") |> rename(isp = ipinfo_org) |> mutate(source = "ipinfo")
)
isp_counts
```

**AC note:** Note that with these updates and with the new example data, every case got flagged for geo_disagree. Might want to work on finding a better way to do this that's more precise. It's inherently kind of hard because two city names might not be exactly the same, but they might be neighboring cities and therefore be fine, so kind of difficult to automate.

### Without flagging by city

```{r,eval=F}
# suspicious location flag
combined_results <- combined_results |>
  mutate(
    geo_outside_us = (ipapi_country != "United States" | ipinfo_country != "US" | ipquery_location.country != "United States"),
    geo_disagree = (ipapi_regionName != ipinfo_region |
                      ipapi_regionName != ipquery_location.state | # seems kind of equivalent but not quite the same
                                            ipinfo_region != ipquery_location.state) # seems kind of equivalent but not quite the same
    )

combined_results$geo_disagree # in this instance, all of these are getting flagged

isp_counts <- bind_rows(
  combined_results |> count(ipapi_isp,  name = "n") |> rename(isp = ipapi_isp) |> mutate(source = "ipapi"),
  combined_results |> count(ipinfo_org, name = "n") |> rename(isp = ipinfo_org) |> mutate(source = "ipinfo")
)
isp_counts
```
Most are still getting flagged

### Without flagging by region




```{r}
# join to original data
d_ips <- ip_locations_raw |>
  mutate(ip_address = as.character(ip_address) |> str_trim()) |>
  left_join(combined_results, by = c("ip_address" = "query"))
d_ips
```

```{r}
# duplicate IP address flag
d_ips  <- d_ips  |>
  add_count(ip_address, name = "ip_count") |>
  mutate(dup_ip = ip_count > 1)
table(d_ips$dup_ip)

# check for clustering around the same finish time
# note: doesn't seem super useful
# time_clusters <- d_ips |>
#   group_by(duration_in_seconds) |>
#   summarise(count = n(), .groups = "drop") |>
#   arrange(desc(count))

# bot suspicion score
# note: I would add qualtrics relevantID/recaptcha and open-ended response flags to this (if available in your data)
d_ips <- d_ips |>
  mutate(
    bot_score = (suspicious_host + geo_outside_us + geo_disagree + dup_ip)
  )
table(d_ips$bot_score)
```

# Additional Sleuthing Steps

**AC note:** If we want to incorporate these remaining steps into the final code, we could add some sample open-ended data and Qualtrics RelevantID data into our sample data. For now, I'm setting it not to run

```{r,eval=F}
# open text as positive (less likely to be a bot)

## MM's version:
# d_ips <- d_ips |>
#   mutate(
#     n_open_text = rowSums(across(
#       c(park_do_5_text, metastereotype_8_text, stereotypes_8_text,
#         activities_do, activities_where, city_state, us_zip_code,
#         profession, feedback, free_stereotypes, free_stereotype_you,
#         soc_stereotypes_8_text, education_10_text),
#       ~ !is.na(.x) & .x != ""
#     ))
#   )

## AC's version (with OE variables from SES Data)
## do something else with this part? should this be added to bot score?
d_ips <- d_ips |>
  mutate(
    n_open_text = rowSums(across(
      c(ethnicity_5_text,
        gender_open,
        formative_yrs,
        political_orient_1,
        sex_orient_open,
        comments),
      ~ !is.na(.x) & .x != ""
    ))
  )
table(d_ips$n_open_text)

# AC: examine responses with 0 blank open-ended Qs
# **all of these response with 0 blank OEs either were screened out or otherwise did not finish**
# doesn't seem super useful
d_ips %>% filter(n_open_text==0) %>% select(ip_address,bot_score,suspicious_host,geo_outside_us,geo_disagree,dup_ip)
d_ips %>% filter(is.na(bot_score))
d_ips %>% filter(n_open_text>=1 & bot_score==0) 
d_ips %>% filter(n_open_text>=1 & bot_score<2) 
table(d_ips$n_open_text)

### iii. Qualtrics bot flagging tools

# RelevantID fraud score

# For fraud score, Qualtrics indicates that any score >30 is likely fraudulent and a bot. I'll also make a second flag to indicate any scores that are >0.

d_ips <- d_ips %>% mutate(rel_id_fraud_flag = ifelse(q_relevant_id_fraud_score >= 30, 
                                            TRUE,
                                            FALSE))
table(d_ips$rel_id_fraud_flag)

d_ips <- d_ips %>% mutate(rel_id_fraud_flag_0 = ifelse(q_relevant_id_fraud_score > 0, 
                                            TRUE,
                                            FALSE))
table(d_ips$rel_id_fraud_flag_0)

d_ips %>% filter(is.na(q_relevant_id_fraud_score)) # no missing scores

d_ips <- d_ips |>
  mutate(
    bot_score_relid = (suspicious_host + geo_outside_us + geo_disagree + dup_ip + rel_id_fraud_flag)
  )
table(d_ips$bot_score_relid)
table(d_ips$bot_score)
bot_ids_relid <- d_ips %>% filter(bot_score_relid>=2)
```

